Title Goes Here

### 2024-05-06 analysis/paper/paper.qmd
stash
28 for all panel plots

ggplot() +
  geom_smooth(data =  jobdata_topic_year_tally,
            aes(year_ad_posted,
                prop,
                group = name,
                colour = name),
            size = 3,
           span = 0.7,
            se = FALSE) +
  xlab("Year") +
  ylab("Proportion of all ads") +
  scale_colour_brewer(palette = "Dark2") +
  guides(colour = guide_legend("Topic\nfocus",
                               label.position = "bottom")) +
    theme_minimal( base_size = 14) +
  theme(legend.position="bottom")

@@

@@

ggplot() +
  geom_smooth(data =  jobdata_method_year_tally,
            aes(year_ad_posted,
                prop,
                group = name,
                colour = name),
            size = 3,
           span = 0.7,
            se = FALSE) +
  xlab("Year") +
  ylab("Proportion of all ads") +
  guides(colour = guide_legend("Method\nfocus",
                               label.position = "bottom")) +
    theme_minimal( base_size = 14) +
  theme(legend.position="bottom")

>>>>

ggplot() +
  geom_smooth(data =  jobdata_topic_year_tally,
            aes(year_ad_posted,
                prop,
                group = name,
                colour = name),
            size = 3,
           span = 0.7,
            se = FALSE) +
  xlab("Year") +
  ylab("Proportion of all ads") +
  scale_colour_brewer(palette = "Dark2") +
  guides(colour = guide_legend("Topic\nfocus",
                               label.position = "bottom")) +
    theme_minimal( base_size = 28) +
  theme(legend.position="bottom")

@@

# how many times each topic mentioned?
jobdata_method_year_tally_max %>%

  ggplot() +
  aes(reorder(name, n),
      n)+
  geom_col() +
  xlab("") +
  theme_minimal() +
  coord_flip()

@@

ggplot() +
  geom_smooth(data =  jobdata_method_year_tally,
            aes(year_ad_posted,
                prop,
                group = name,
                colour = name),
            size = 3,
           span = 0.7,
            se = FALSE) +
  xlab("Year") +
  ylab("Proportion of all ads") +
  guides(colour = guide_legend("Method\nfocus",
                               label.position = "bottom")) +
    theme_minimal( base_size = 28) +
    scale_colour_brewer(palette = "Dark2") +
  theme(legend.position="bottom")
